Semiconductor equity markets exhibit frequent regime shifts, heightened volatility, and pronounced sensitivity to macroeconomic and geopolitical shocks. Events such as supply chain disruptions, U.S.--China policy tensions, and cyclical demand swings have consistently revealed the shortcomings of static risk models in this sector. Conventional approaches often fail to keep pace with rapidly changing market dynamics, leading to unmanaged drawdowns and inefficient portfolio allocations.

This paper presents a hybrid regime detection and dynamic risk overlay framework specifically designed for semiconductor equities. Our approach fuses Hidden Markov Models (HMMs) and Long Short-Term Memory (LSTM) networks to identify latent market regimes, combining their outputs via entropy-weighted Bayesian model averaging. These regime probabilities drive a real-time risk management system that dynamically adjusts position sizing based on volatility, drawdown, and model confidence.

Applied to a five-year out-of-sample portfolio (2019--2024), the proposed framework delivers more than a 50\% reduction in volatility and an approximate 15 percentage point improvement in maximum drawdown relative to passive and static strategies---without a significant sacrifice in returns. While not intended as an alpha-generating strategy, the system serves as a deployable overlay for institutional portfolios seeking dynamic de-risking and enhanced risk-adjusted resilience.

The architecture is modular, interpretable, and production-ready, enabling real-time regime classification, signal integration, and stress testing. Consequently, it offers tangible value for asset managers navigating volatile, regime-sensitive environments such as the semiconductor industry.
